\documentclass[11pt,a4paper]{article}
\usepackage[left=2cm,text={17cm,25cm},top=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\graphicspath{ {figs/} }

\begin{document}

\begin{center}
	\LARGE{Soft Computing}\\
	\Large{Job Performance Evaluation Using Back-propagation Network}
	\vspace{0.5cm}

    \begin{centering}
    \small{
        Bc. Petr Stehlík <xstehl14@stud.fit.vutbr.cz>
        }
    \end{centering}

	\vspace{0.2cm}

\end{center}

\section{Introduction}
Every user of a supercomputer needs to know whether their submitted job finished successfully and performed well. So far these tedious tasks are usually performed manually using only the output of their program and over-simplified metrics such as job runtime and utilized resources.

The aim of this project is to create a back-propagation neural network which can classify a job run whether it run well or it was in some way suspicious of unwanted behaviours such as poor performance or execution failure.

The network itself is supplied with fine-granular metric data acquired via Examon framework\cite{examon} which was run on Galileo supercomputer located in CINECA, Bologna, Italy. Where all job and metric data were gathered.

The structure of this document is as follows: in section \ref{sec:theory} the theoretical background needed for this project is presented together with the description of Examon framework. In the following section \ref{sec:data} the data supplied to the network are described as well as the final format of the data. Afterwards, in section \ref{sec:implementation} the implementation of the network and its structure are laid out and in the last two sections \ref{sec:res} and \ref{sec:sum} the achieved results, summary and further work are discussed.

\input{theory}

\input{data}

\input{implementation}

\section{Achieved Results}
\label{sec:res}

\section{Summary}
\label{sec:sum}

As a proof of concept for classifying jobs on HPC cluster it was verified that such classificator can be made using a set of backpropagation networks. With rather small dataset to train and evaluate on the error rate wasn't minimal and can be further reduced using a larger labelled dataset and users' feedback.

Using the intermediate input from metric networks it can be used for intelligent dashboards in Examon Web where only suspicious metrics can be shown in combination with several fixed ones.

This work is the base for my master thesis and will be further expanded to provide complex insights on users' jobs.

\subsection*{Acknowledgements}
This work was done using the Examon framework created by F. Beneventi, A. Bartolini, A. Borghesi and collective at UNIBO, Italy. Examon Web was created by P. Stehlík during the PRACE Summer of HPC stay at CINECA, Bologna, Italy. Data used in this project were collected using the CINECA infrastructure and Galileo supercomputer and anonymized before any use in this project.

\bibliography{doc}{}
\bibliographystyle{abbrv}

\end{document}
